Review: SASB SAT Solving for Vesicle Traffic Systems in Cells

### 2018-04-15 papers/sabs-2017/paper/bio.tex

\textbf{The cell as a transport graph:} We consider a cell to be a
collection of compartments (nodes) and vesicles (edges), thus defining
a transport graph.
%
Compartments represent the large membrane-bound organelles, which are
connected by constant fluxes of small transport vesicles.
%
Every compartment or vesicle has a set of molecules associated with
it.
%
These include SNAREs and other biomolecules that regulate membrane
traffic, or that play the role of passive cargo.
%
Here we consider an abstract set of molecules and do
not explicitly associate them with particular protein varieties.\textbf{But consider them to be either of  
the two categories Q and R.}
\textbf{Molecular flows and steady state:} The total amount of each
molecular type on each compartment can increase or decrease: this is
due to gain or loss of that molecular type driven by incoming or
outgoing vesicles.
%
Each edge is thus associated with a flux of all the molecular types
carried by the corresponding vesicle.
%
We assume the cell is in a steady state where each compartments
composition does not vary over time, meaning that all incoming and
outgoing fluxes are balanced for each molecular type at each
compartment.

@@

We test many different versions of molecular
regulation.
%
Most generally, the activity state of a given molecule can be a
Boolean function of all the molecular types on a compartment or vesicles.
We have also tested a particularly simple regulation mechanism in which two
molecules that can pair to drive fusion inhibit one another.
%
This is motivated by the idea that pairing must generate an inactive
bi-molecular complex.

\textbf{Synthesis:} We now combine all the above ingredients.
%
Given a particular
transport graph, a particular labeling of all the compartments and edges,
a particular fusion pairing matrix, and a particular regulatory model we do
the following.
\begin{enumerate}
\item We determine which molecules are ``active" on every
compartment or vesicle.
\item or every vesicle fusing to a compartment, we
determine whether there exists an active pair (one molecule on the vesicle,
one on the compartment) which drives that fusion event.
\item For every vesicle-compartment pair where the vesicle does not fuse to the
compartment, we verify that there is no pairing of active molecules on the
vesicle and compartment that could drive their fusion.
\item We verify that every molecular type entering a compartment also leaves the compartment,
and also that every molecular type entering a set of compartments also
leaves that set; this is the steady state condition.
%
This tells us that the
particular graph and molecular labeling does represent an allowed steady
state configuration of a VTS.
\end{enumerate}
%The fusion is a process where SNAREs on the vesicles target compartment is driven by the zipping together of vesicle
%and compartment SNAREs [8, 9].
%The SNAREs can be 
%Typically a Q-SNARE triple-helix is confined to one mem-
%brane surface (e.g the compartment), while an R-SNARE single helix is confined to its fusion
%partner (e.g. the vesicle). When these two types of SNAREs are in close proximity they zip
%together into a four-helix bundle, forcing the vesicle to fuse with the compartment. There are
%many types of Q-SNAREs and R-SNAREs spread between different vesicles and compart-
%ments. Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%contain higher numbers (humans have 41) [12]. Only certain Q and R-SNARE combinations
%can zip into complexes, regulating precisely which vesicles fuse with which targets. For our
%analysis, we consider a Q-SNARE triple helix as a single complex and the R-SNARE as its cog-
%nate partner. We refer to zipping as SNARE pairing.

>>>>

\textbf{The cell as a transport graph:} We consider a cell to be a
collection of compartments (nodes) and vesicles (edges), thus defining
a transport graph.
%
Compartments represent the large membrane-bound organelles, which are
connected by constant fluxes of small transport vesicles.
%
Every compartment or vesicle has a set of molecules associated with
it.
%
These include SNAREs and other biomolecules that regulate membrane
traffic, or that play the role of passive cargo.
%
Here we consider an abstract set of molecules and do
not explicitly associate them with particular protein varieties.\textbf{But consider them to be either of  
the two categories Q and R.}
\textbf{Molecular flows and steady state:} The total amount of each
molecular type on each compartment can increase or decrease: this is
due to gain or loss of that molecular type driven by incoming or
outgoing vesicles.
%
Each edge is thus associated with a flux of all the molecular types
carried by the corresponding vesicle.
%
We assume the cell is in a steady state where each compartments
composition does not vary over time, meaning that all incoming and
outgoing fluxes are balanced for each molecular type at each
compartment; this is the \textit{stability condition}.

@@

We test many different versions of molecular
regulation.
%
Most generally, the activity state of a given molecule can be a
Boolean function of all the molecular types on a compartment or vesicles.
We have also tested a particularly simple regulation mechanism in which two
molecules that can pair to drive fusion inhibit one another; this is the \textit{pairing inhibition}.
%
This is motivated by the idea that pairing must generate an inactive
bi-molecular complex.

\textbf{Synthesis:} We now combine all the above ingredients.
%
Given a particular
transport graph, a particular labeling of all the compartments and edges,
a particular fusion pairing matrix, and a particular regulatory model we do
the following.
\begin{enumerate}
\item We determine which molecules are ``active" on every
compartment or vesicle.
\item or every vesicle fusing to a compartment, we
determine whether there exists an active pair (one molecule on the vesicle,
one on the compartment) which drives that fusion event.
\item For every vesicle-compartment pair where the vesicle does not fuse to the
compartment, we verify that there is no pairing of active molecules on the
vesicle and compartment that could drive their fusion.
\item We verify that every molecular type entering a compartment also leaves the compartment,
and also that every molecular type entering a set of compartments also
leaves that set.
%
This tells us that the
particular graph and molecular labeling does represent an allowed steady
state configuration of a VTS.
\end{enumerate}
%The fusion is a process where SNAREs on the vesicles target compartment is driven by the zipping together of vesicle
%and compartment SNAREs [8, 9].
%The SNAREs can be 
%Typically a Q-SNARE triple-helix is confined to one mem-
%brane surface (e.g the compartment), while an R-SNARE single helix is confined to its fusion
%partner (e.g. the vesicle). When these two types of SNAREs are in close proximity they zip
%together into a four-helix bundle, forcing the vesicle to fuse with the compartment. There are
%many types of Q-SNAREs and R-SNAREs spread between different vesicles and compart-
%ments. Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%contain higher numbers (humans have 41) [12]. Only certain Q and R-SNARE combinations
%can zip into complexes, regulating precisely which vesicles fuse with which targets. For our
%analysis, we consider a Q-SNARE triple helix as a single complex and the R-SNARE as its cog-
%nate partner. We refer to zipping as SNARE pairing.

### 2018-04-15 papers/sabs-2017/review-sasb-sat/main.tex

As far as I understood, the method allows to identify one graph (if any) ; \textbf{it would be interesting to consider counting the number of solutions as well.}\newline
{\color{red}{Ashutosh}}

@@

Please find more detailed comments below:\\
\begin{enumerate}
\item one sentence of the abstract is misleading: "what are all possible networks for
various combinations of those properties?" what you actually do is finding ONE
network (i.e. a model satisfying the SMT problem), not all networks. Consider
rephrasing this.\newline
\todo{We should discuss how to rephrase this or stay as it is.}
{\color{red}{Ashutosh.}}\\

@@

\item Definition 1: shouldn't it be $E \subseteq N \times ... $(not the other way round)? \newline
{\color{red}{Ashutosh}}\\

\item the definition of well-structured network deserves better explanation: what does
"equal partitions" mean? partitions with the same num of elements? the second
condition would be clearer if you added an explanation.\newline
{\color{red}{Ashutosh}}\\

\item - \todo{We should add to the definition. This reviewer have read things in detail} Do you allow self-edges in G? I see that you later add constraints to avoid that, but I've missed this point from definition 1\newline
{\color{red}{Ankit, Ashutosh}}\\

\item Definition of connectedness for G: do you allow any path, or it must exist $m \in M$ such that for all n,n', n' is m-reachable from n? this is not clear at this point
and should be improved. \newline
{\color{red}{Ashutosh}}\\

\item Since you use uninterpreted functions, I guess you can no longer say that you use
SAT, \todo{valid point should be addressed} but you are using SMT (the theory being that of uninterpreted functions).\newline
{\color{red}{Srivas, Ankit, Ashutosh}}\\

\item Eq. V1: I don't get why you use implication and not double implication \newline
{\color{red}{Ashutosh}}\\

>>>>

As far as I understood, the method allows to identify one graph (if any) ; \textbf{it would be interesting to consider counting the number of solutions as well.}\newline
{\color{red}{done.}}

@@

Please find more detailed comments below:\\
\begin{enumerate}
\item one sentence of the abstract is misleading: "what are all possible networks for
various combinations of those properties?" what you actually do is finding ONE
network (i.e. a model satisfying the SMT problem), not all networks. Consider
rephrasing this.\newline
\todo{We should discuss how to rephrase this or stay as it is.}
{\color{red}{done.}}\\

@@

\item Definition 1: shouldn't it be $E \subseteq N \times ... $(not the other way round)? \newline
{\color{red}{done.}}\\

\item the definition of well-structured network deserves better explanation: what does
"equal partitions" mean? partitions with the same num of elements? the second
condition would be clearer if you added an explanation.\newline
{\color{red}{done.}}\\

\item - \todo{We should add to the definition. This reviewer have read things in detail} Do you allow self-edges in G? I see that you later add constraints to avoid that, but I've missed this point from definition 1\newline
{\color{red}{it was already written in the definition of well-structured}}\\

\item Definition of connectedness for G: do you allow any path, or it must exist $m \in M$ such that for all n,n', n' is m-reachable from n? this is not clear at this point
and should be improved. \newline
{\color{red}{done.}}\\

\item Since you use uninterpreted functions, I guess you can no longer say that you use
SAT, \todo{valid point should be addressed} but you are using SMT (the theory being that of uninterpreted functions).\newline
{\color{red}{Ankit will replace everywhere from SAT to SMT}}\\

\item Eq. V1: I don't get why you use implication and not double implication \newline
{\color{red}{Ashutosh. needs thinking?? }}\\
